### 2022-11-10 NSF2022/Description/specificaim1v2.tex
more BG mods

\section{Specific Aim 2: Membrane vesicles as self-organized granules}
\subsection{Prior work related to the proposal.}

@@

>>>>

\section{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specific_aim1}
\subsection{Prior work related to the proposal.}

@@

A natural questions concerns the well-posedness
\eqref{eq:RBT}--\eqref{eqn:stressbalance}
and its generalizations. A recent and strongly developing direction in
the area of nematics liquid crystals concerns the interaction of
Landau de Gennes functionals like \eqref{eq:energy_law} with colloids
\cite{doi:10.1098/rsta.2020.0432}.
In this spirit, a first step to understand the effect of the flow
in our model is to obtain some solid well-posedness results.

\begin{quotation}
  \textbf{Problem 1.} Consider a collection the closed,
  disjoint granules $U_i$ with smooth boundary,
with no-slip, rigid body motion boundary conditions.
Assume a either a single or double well potential
and a smooth phase field boundary condition.  
Study the well-posedness of the coupled system
\eqref{eq:RBT}--\eqref{eqn:stressbalance}
for short times.  For global in time solutions, determine
whether lubrication forces ensure positive distance
between granules.  Describe the behaviour in the limit
zero screening length limit.  
\end{quotation}

This problem is attractive because combines the diffusive interface
effects involving a free boundary in aqueous part of the region \cite{}
with interfacial effects coming from the long range inter-granual
attraction. Generalizations of Problem 1 include modifying the 
system to account for various time scales.
We may consider, for example, modifying \eqref{eqn:phase}
to include transport of the phase field by the background fluid;
\begin{equation*}
\phi_t + \uu \cdot \nabla = -\lambda \frac{\delta E}{\delta \phi} = \lambda(\epsilon^2 \Delta \phi - W'(\phi))
\end{equation*}
The modified systems enjoys the same energy law as \eqref{eq:energy_law} 
except that there will be an addtional dissipation term coming from the
Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$.

The second problem we consider concerns the approximation
of equilibrium elastic energy of curves and surfaces.
We have compared two-dimensional configurations of amphiphilic granules
to membrane configurations found in continuum mechanics.
The simulations results in~\cite{Fu2018_SIAM,FuQuRyYo22}
showed that the granular bilayers 
basically replicated the elastic energies for bending, tilt, and
stretching
but we do not yet have any analytical evidence to support this conclusion.
To understand the approximation mathematically, we take the following:
\begin{quotation}
  \textbf{Problem 2.} Place a collection of
  amphiphilic granules
with equally spaced centers along a curve $\mathcal{C}$.
For simplicity, assume that the directors are normal to the curve
and that the granules are all disks with radius proportional to $\epsilon$. 
Study the sharp interface limit of the energy $E$ 
relative to that of an array of granules placed along a flat curve. 
In this limit, the number of granules $N_b$ goes to infinity
to ensure equal spacing.
Study how the bending the bending $k_B$ and stretching $k_A$ coefficients
depend on the granual size relative to their spacing.
Generalize the problem to account for aspect ratio of elliptical granules
and nonzero tilt. 
\end{quotation}
Given the relatively complicated geometry consising
of a plane with a number of disjoint disks removed, 
we can start by approaching the problem in a simplified
setting such as when the reference curve is a circle.
There is a large body work in this direction for nematics
studying either the case of a single coloidal particle and
the qualitative structure of defects around it
\cite{Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}
many particles and the homogenization effects
\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919,BERLYAND200597,doi:10.1137/130910348}.
A closely related area that consider similar analysis
dimension reduction for
Landau-de Gennes models on curved nematic confined to thin films
\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,doi:10.1142/S0218202516500470, FoFrLe07}.
